Improving the Replicability of Psychological Science Through Pedagogy

### 2017-05-18 paper/paper.Rmd
Fix Fig. 2 legends, color schemes

```{r, fig.cap="Replication effect size (A) and Bayes factor (B), plotted by the original effect size and Bayes factor, respectively. Point size shows replication N (A) and ratio of test degrees of freedom (B), color indicates subjective replication assessments by the authors. Note that the key statistic for one replication was a multivariate $F$ test, hence a comparable default Bayes factor could not be computed. Additionally, the original Bayes factor for oen finding was many orders of magnitude greater than the others so it is not displayed.", fig.pos="ht", fig.height=3.6}

p1 <- ggplot(d,aes(x=original_ES_d,y=rep_es)) +
  geom_point(alpha = .8, 
             aes(color=replicated_TA_factor, size = collected_n)) +
  # geom_text_repel(aes(label = first_author_name), size = 2, force = 2) +
  scale_x_continuous(limits = c(0, 1), 
                breaks = c(.1, .3, .5, .7, .9)) +
  scale_y_continuous(limits = c(0, 1), 
                breaks = c(.1, .3, .5, .7, .9)) +
  geom_abline(slope = 1, intercept = 0, linetype = 2) +
  geom_smooth(method = "lm", se=FALSE) +
  xlab("Orig. effect size (r)") + 
  ylab("Rep. effect size (r)") + 
  theme_bw(base_size=10) + theme(legend.position="bottom") + 
  scale_size(name = "Rep. N") +
  # scale_color_solarized(guide = FALSE)
  scale_color_solarized(name = "Subj. rep. rating")

@@

p2 <- ggplot(tstatDF, aes(x = origBF, y = repBF)) +
  geom_point(alpha = .8, aes(size = df_ratio, 
                             col = replicated_TA_factor)) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_abline(slope = 1, intercept = 0, linetype = 2) +
  xlab("Orig. Bayes Factor") + 
  ylab("Rep. Bayes Factor") + 
  scale_x_log10(limits = c(10**-1.75, 10**11), 
                breaks = c(1/10, 1, 10, 100, 1e+3, 1e+6, 1e+9),
                labels = c(".1", "1", "10","100", "1e3", 
                           "1e6","1e9")) +
  scale_y_log10(limits = c(10**-1.75, 10**11),
                breaks = c(1/10, 1, 10, 100, 1e+3, 1e+6, 1e+9),
                labels = c(".1", "1", "10","100", "1e3", 
                           "1e6","1e9")) + 
  theme_bw(base_size=10) + theme(legend.position="bottom") + 
  scale_size_continuous(breaks=c(.5, 2, 5),name = "Rep. df/Orig. df") + 
  scale_color_solarized(name = "Subj. rep. rating") +
  guides(size=guide_legend(order = 1), 
         color=guide_legend(order = 2))

plot_grid(p1, p2, labels = c("A", "B"))
```

>>>>

```{r, fig.cap="Replication effect size (A) and Bayes factor (B), plotted by the original effect size and Bayes factor, respectively. Point size shows replication N (A) and ratio of test degrees of freedom (B), color indicates subjective replication assessments by the authors. Note that the key statistic for one replication was a multivariate $F$ test, hence a comparable default Bayes factor could not be computed. Additionally, the original Bayes factor for one finding was many orders of magnitude greater than the others so it is not displayed.", fig.pos="ht", fig.height=3.6}

# Want semantically meaningful values for coding values
colorMap <- c('No'='red', 'Partial'='#b58900', 'Yes'='green4')

p1 <- ggplot(d,aes(x=original_ES_d,y=rep_es)) +
  geom_point(alpha = .8, 
             aes(color=replicated_TA_factor, size = collected_n)) +
  # geom_text_repel(aes(label = first_author_name), size = 2, force = 2) +
  scale_x_continuous(limits = c(0, 1), 
                breaks = c(.1, .3, .5, .7, .9)) +
  scale_y_continuous(limits = c(0, 1), 
                breaks = c(.1, .3, .5, .7, .9)) +
  geom_abline(slope = 1, intercept = 0, linetype = 2) +
  geom_smooth(method = "lm", se=FALSE, colour="#657b83") +
  xlab("Orig. effect size (r)") + 
  ylab("Rep. effect size (r)") + 
  theme_bw(base_size=10) + theme(legend.position="bottom", aspect.ratio = 1) + 
  scale_size(name = "Rep. N") +
  scale_color_manual(values = colorMap, guide = FALSE)  +
  #scale_color_solarized(name = "Subj. rep. rating") +
  guides(size=guide_legend(order = 1, direction = "horizontal", byrow=TRUE))

@@

p2 <- ggplot(tstatDF, aes(x = origBF, y = repBF)) +
  geom_point(alpha = .8, aes(size = df_ratio, 
                             col = replicated_TA_factor)) +
  geom_smooth(method = "lm", se = FALSE, colour="#657b83") +
  geom_abline(slope = 1, intercept = 0, linetype = 2) +
  xlab("Orig. Bayes Factor") + 
  ylab("Rep. Bayes Factor") + 
  scale_x_log10(limits = c(10**-1.75, 10**11), 
                breaks = c(1/10, 1, 10, 100, 1e+3, 1e+6, 1e+9),
                labels = c(".1", "1", "10","100", "1e3", 
                           "1e6","1e9")) +
  scale_y_log10(limits = c(10**-1.75, 10**11),
                breaks = c(1/10, 1, 10, 100, 1e+3, 1e+6, 1e+9),
                labels = c(".1", "1", "10","100", "1e3", 
                           "1e6","1e9")) + 
  theme_bw(base_size=10) + 
  scale_size_continuous(breaks=c(.5, 2, 5),name = "Rep. df/Orig. df") + 
  scale_color_manual(values = colorMap, guide = F) +
  theme(legend.position="bottom", aspect.ratio = 1) + 
  guides(size=guide_legend(direction = 'horizontal'))

plotrow <- plot_grid(p1, p2, labels = c("A", "B"))
legend <- get_legend(
  p2 + 
    theme(legend.position="bottom") + 
    guides(color = guide_legend(title = "Subjective replication rating", 
                                direction = 'horizontal'),
           size = FALSE)
)
plot_grid(plotrow, legend, ncol = 1, rel_heights = c(1, .2))
```
